Self-assembly of colloid-cholesteric composites provides a possible route to switchable optical materials

### 2014-03-05 trunk/papers/2012-sandwich/support.tex
Correct spelling
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2328 40876441-3496-0410-a613-a2fca35b2ae2

For simplicity,  the size of the BPI unit cell is not allowed to 
readjust dynamically to minimize free energy (there is no 
``redshift''~\cite{blue1}): this would lead to quantitatively different 
values of the free energy, but qualitatively similar structures.

>>>>

For simplicity,  the size of the BPI unit cell is not allowed to 
readjust dynamically to minimise free energy (there is no 
``redshift''~\cite{blue1}): this would lead to quantitatively different 
values of the free energy, but qualitatively similar structures.
